ZCB Pricing

### 2018-10-19 ZCB Pricing .Rmd
New comments and final code

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i,j-1]# Discretize the SDE of the interest model using Euler Discretization to simulate rates over discrete sub-intervals
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

@@

  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using negative values of RV
  sim_path[1,] = r
  sim_path_inv[1,] = r

@@

  for (i in 1:n){

    for (j in 2:(s+1)){
      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i,j-1] # Same Euler Discretization as in the Crude Monte Carlo function
      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i,j-1] # Euler Discretization for the use of -Z_i
      sim_path[j,i] =sim_path[j-1,i]+dr
      sim_path_inv[j,i] = sim_path_inv[j-1,i]+dr_i

@@

}
# The control variate estimate is taken as the difference between the the Crude Monte Carlo estimates of the Vasicek and CIR model plus the closed form solution of the CIR model

@@

compare_mat[,2] <- bond_price()

@@

library(xtable) # package to get LaTex code for table
xtable(compare_mat, digits = 5)

@@

senses[,2:9] <-round(as.numeric(senses[,2:9]), digits=5)
library(xtable)
xtable(senses, digits = 5)
```

@@

VarCR=var(CR) # variance of crude monte carlo
VarAN=var(AN) # variance of antithetic variates
VarMM=var(MM) # variance of moment matching
varCV=var(CV) # variance of control variates

>>>>

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i,j-1]# Discretize the SDE of the interest model using the Euler Discretization to simulate rates over discrete sub-intervals
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

@@

  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using negative values of RV
  sim_path[1,] = r # Inital rates on first row
  sim_path_inv[1,] = r

@@

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i,j-1] # Same Euler Discretization as in the Crude Monte Carlo function
      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i,j-1] # Euler Discretization for the use of -Z_i
      sim_path[j,i] =sim_path[j-1,i]+dr
      sim_path_inv[j,i] = sim_path_inv[j-1,i]+dr_i

@@

}
# The Control Variate estimate is taken as the difference between the the Crude Monte Carlo estimates of the Vasicek and CIR model plus the closed form solution of the CIR model

@@

compare_mat[,2] <- bond_price() # Known solution bond price

@@

library(xtable) # package to get LaTex code for table
xtable(compare_mat, digits = 5) # Output of LaTex code for table

@@

senses[,2:9] <-round(as.numeric(senses[,2:9]), digits=5)
library(xtable) 
xtable(senses, digits = 5) # Table for data on sensitvity tests found in appendix B
```

@@

VarCR=var(CR) # variance of Crude Monte Carlo
VarAN=var(AN) # variance of Antithetic Variates
VarMM=var(MM) # variance of Moment Matching
varCV=var(CV) # variance of Control Variates
